Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-20 article.rnw
Add a missing reference.

%Several methods have been applied to regularise species interaction models, each with their own limitations.
%For example, it is often assumed that most pairs of species don't interact, setting many of the parameters to zero \parencite{mutshinda2009drives,ovaskainen2017species}.
%TODO: Find a citation for why this assumption doesn't hold.

One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}. %TODO: XXX why this could be a problem XXX.
Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.

>>>>

One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
%TODO: XXX why this could be a problem XXX.
Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
